### 2019-01-29 README.Rmd

``` r
# install.packages("devtools")
devtools::install_github("dynverse/dynbenchmark")
```

@@

```{r, message = TRUE, echo = TRUE}
dynwrap::test_docker_installation(detailed = TRUE)
```

>>>>

``` r
# install.packages("devtools")
devtools::install_github("dynverse/dynbenchmark/package")
```

@@

```{r, message = FALSE, echo = TRUE}
dynwrap::test_docker_installation(detailed = TRUE)
```
